TBD

### 2020-11-03 outputs/paper/paper1.Rmd

In this report, we will be forecasting the winner of the upcoming US Presidential Elections 2020 between incumbent Donald Trump of the Republican Party and Joe Biden of the Democratic Party, by looking at different factors that affect a citizen’s voting intentions leading to Election Day. We cleaned the Nationscape dataset and closely examine the variables age, race, household income, and vote which will form the basis of our election prediction. Then we used an MRP model (a combination of multilevel logistic regression and post-stratification) to analyse the factors and it also helps us in achieving a much narrower confidence interval for our prediction. After our analysis, we concluded that Joe Biden will win the overall popular vote of the 2020 American presidential election.

@@

The United States 2020 Presidential Election is considered by many to be one of the most crucial elections in recent history. American voters will be deciding to elect Democratic Leader, Joe Biden or Republican leader, Donald Trump. In this report, we will be forecasting the results of the US 2020 election using multi-level regression with post stratification.

We are interested in finding out who will win the overall popular vote in the US 2020 election between Donald Trump and Joe Biden. To begin, we started by cleaning the dataset provided by Nationscape. The data we are using was collected from June 25th, 2020 to July 1st, 2020. Using the dataset, we plan to closely analyze the following variables to use them as predictors in predicting the results of the 2020 US election:

-	age (discloses age of respondent)
-	race_ethnicity (discloses race of respondent)
-	household_income (discloses household income of respondent)
-	trump_biden (discloses who the respondent will vote for in the 2020 election)

After using multi-level regression with post stratification, we determined that Joe Biden will be the winner of the US 2020 Election. Predicting the results of the US 2020 election is important because it helps give those residing in the USA certainty about who their next president will be. Information about the winner of the election is highly sought after because it can be used to predict upcoming policy. This is useful for individuals and organizations when planning their lives and can have a large impact on the rights of some individuals.  Additionally, collecting information related to the election allows us to analyze different demographic groups and determine how they are voting to further identify areas they find important; this information is important from a policy design perspective and also to analyze how society is interacting.

In this report, we will begin by discussing with a detailed look at the dataset we are analyzing, followed by a look at the modeling of our results. Lastly, we will discuss the results of our analysis and also include an appendix to display any extraneous information.

@@

The variables that we used in our dataset are as follow:

- age
     o	Asks the question “What is your age?”
     o	It provides an integer value greater than or equal to 18 
- household_income
     o	Asks the question “What is your current annual household income before taxes?" 
     o	Provides an extensive list of options beginning with $5,000 increments and then increases to $25,000 increments. We         later grouped the options into larger bins making it simpler to understand and easier to analyze
     o	This is the variable in our dataset that many people did not feel comfortable answering and was left as N/A. When           cleaning the dataset, we removed all responses that left this answer as N/A  
- race_ethnicity
     o	Asks the question “What is your race?”
     o	An extensive list of options are provided for the respondent to disclose their race. Because the list is very               extensive, we decided to group the options into larger bins making to simpler to understand and easier to analyze. 
- trump_biden
     o	Asks the question “If the general election for president of the United States was a contest between Joe Biden and           Donald Trump, who would you support? “ 
     o	Options are either ‘Joe Biden’, ‘Donald Trump’, or ‘Don’t Know’

We created an additional variable called ‘binary’ which outputs the result of the variable ‘trump_biden’ as a 1 or a 0 making it binary, therefore easier to analyze. Since some variables had an extensive list of options (e.g. age, household income, race), we grouped the responses for those variables so that they are simpler and easier to analyze.

To develop a sense of familiarity with the dataset, we will closely examine some of the variables we will be analyzing in the dataset.

@@

In Figure [] below, we will examine the variable 'household_income' and we can see that our data is largely skewed towards households with income less than $50,000:
```{r}
# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
incomeinfo <- tbdata %>% group_by(household_income_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
incomegraph <- incomeinfo %>% ggplot(aes(x = "", y = prop, fill = household_income_grouped)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Accent") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "Survey Distribution of Household Income", fill="Household Income") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
     theme(text = element_text(size=15))
incomegraph
```
Clearly, those with income less than $50,000 are overrepresented in the dataset as they take up 50% of the responses, therefore it is appropriate to use post stratification on our dataset.

We can see a similar skewed distribution with variable 'race' in Figure [] below:
```{r}
# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
raceinfo <- tbdata %>% group_by(race_ethnicity) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
racegraph <- raceinfo %>% ggplot(aes(x = "", y = prop, fill = race_ethnicity)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Set3") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "Survey Distribution of Respondent Race", fill="What is your race?") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4) +
     theme(text = element_text(size=13))
racegraph
```
It is obvious that the respondents of our survey are primarily white and there is very little representation of minorities.

Lastly, by examining the variable age in Figure [] below, we can see how very little the population 76+ is represented in our dataset. 
```{r}
# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
ageinfo <- tbdata %>% group_by(age_group) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
agegraph <- ageinfo %>% ggplot(aes(x = "", y = prop, fill = age_group)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Set3") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "Survey Distribution of Respondent Age", fill="Age Groups") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4)+
     theme(text = element_text(size=13))
agegraph
```
The fact that those age 76+ make up only 3% of the data could be a product of the fact that the survey was completed online. Clearly, the survey doesn't accurately represent those aged older than 76/ This poses the question — does our data represent the United States?  By looking at the figure above, the answer is no. To adjust for the fact that the population aged 76+, we will use post stratification.

The dataset that we used contains many key features. Many of the variables in the dataset contain an extensive list of options assuring us that the data represents the participant's view accurately. Despite the fact that we cleaned the dataset to make it simpler to view, we still believe that the detailed responses that the participants provided accurately reflect their views on the 2020 election, making our analysis meaningful. Another key feature is the fact that the data was collected over a short period of time— from June 25th, 2020 to July 1st, 2020. This significantly reduces the negative time-based effects that may have affected the data ensuring that all respondents are responding on a similar ground and no one's opinion dramatically differed due to the survey taking place over a large period of time.

The dataset we used contains many strengths and weaknesses. One of the strengths is due to the fact that the survey is distributed online. In today’s age where most things are online, this ensures that we can reach a wide part of the United States. At the same time, this can also be viewed as a weakness because certain age groups of the United States may not be tech-savvy enough to complete an online survey. The older population of the United States (e.g. 75+) may not be able to complete the survey because it is online which means that our data may not accurately reflect the older populations views regarding the 2020 election. A potential solution to this weakness is to use administer multiple forms of the survey to ensure that all people can access the survey.

Another weakness of the data comes from the fact that we use convenience-based sampling which inherently contains bias. Because the sampling method is based on convenience, we may be unlucky when sampling and get a sample group that inaccurately represents the population of the US making our results meaningless. A potential solution to this is to use a random sampling-based method to reduce bias as much as possible.

Lastly another weakness of our dataset is due to the fact that the survey data we are analyzing is collected from June 25th, 2020 to July 1st, 2020. Between July and November (the month of the election), many voters may not have an informed vote and their opinions may still be swayed after watching crucial debates and hearing what the leaders have to say; our data doesn’t take into consideration the people whose votes may change in the most crucial months of the election. A solution to this weakness can be to analyze data that may have occurred closer to the actual election (e.g. September or October) so that the participants have an informed vote.

@@

## Figure 4
```{r}
# read in data
acs <- read_dta("post_strat_data-2.dta")
# label the data as it is a dta
acs <- labelled::to_factor(acs)
#create a tibble that includes counts and proportions based on groups
incomeinfoacs <- acs %>% group_by(household_income_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
#Graph this tibble in a pie graph
incomegraphacs <- incomeinfoacs %>% ggplot(aes(x = "", y = prop, fill = household_income_grouped)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Accent") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "ACS Distribution of Household Income", fill="Household Income") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
     theme(text = element_text(size=15))

@@

## Figure 5
```{r}
#create a tibble that includes counts and proportions based on groups
ageinfoacs <- acs %>% group_by(age_group) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
#Graph this tibble
agegraphacs <- ageinfoacs %>% ggplot(aes(x = "", y = prop, fill = age_group)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Accent") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "ACS Distribution of Respondent Age", fill="Household Income") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
     theme(text = element_text(size=15))

@@

## Figure 6
```{r}
#create a tibble that includes counts and proportions based on groups
raceinfoacs <- acs %>% group_by(race_ethnicity) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
#Graph this tibble in a pie graph
racegraphacs <- raceinfoacs %>% ggplot(aes(x = "", y = prop, fill = race_ethnicity)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Accent") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "ACS Distribution of Respondent Race", fill="Household Income") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
     theme(text = element_text(size=15))

@@

## Table 6
```{r}
#Generate a table that displays the first couple responses from the cell count that was generated for weighting 
Table6 <- post_strat_cellcount_2 %>% 
  dplyr::select(
    age_group, race_ethnicity, household_income_grouped, n, prop
  ) %>% 
  head() %>% 
  kable(align = "c",
        format = "simple",
        col.names = c("Age Group", "Race", "Household Income", "Number of Repondents", "Proportion of Responses"),
        digits = 6
        ) 
Table6
```

@@

```{r include=FALSE}
#Get general percentage of people voting for Trump by Race
aggregate(tbdata[8], list(tbdata$race_ethnicity), mean)
#get overal percentage of people voting for Trump
mean(tbdata$binary)  
```

@@

In conclusion, the findings of this paper suggest that the Biden will win the popular vote and that this is largely due to his appeal among lower income individuals and how he has note ostracized the non-white voter base. This is despite that fact that he is less popular among older individuals who are more likely to vote.

It also suggests that there are important demographic differences between voters that fall along race, class, and age lines. Distinctions that would be important to pick apart in further in depth studies where the reasons for these differences could be further understood now that they have been identified.

However, as always, this analysis could be improved. Looking at popular vote is not the most accurate measure of presidential election in the U.S. One simply has to look to Hilary Clintons loss in 2016 Despite having won the popular vote 48% to Trump’s 45.9% (NY Times 2016). The elections in the United states are decided by the electoral college.

This is a system that assigns each state a certain number of electoral votes 2 for each state and then an additional number of votes based on the population of the state (NCSL 2020). But what does that mean? That the proportion of votes ends up skewed towards smaller states. For example California the most populace state has a population of 39.51 million and 55 electoral college votes. Whereas Wyoming has a population of 578.7 thousand and 3 electoral college votes (NCSL 2020). This means that 1 electoral college vote in California represents 718.4 thousand Californians. While 1 electoral college vote in Wyoming represents 192.9 thousand Wyomingites.

Furthermore, how each state casts their votes also differ some cast the totality of their ballots based upon the popular vote in their state. While others cast ballots based upon how many congressional districts each candidate can win in a first past the post election.

What this means is that for the best forecasting accuracy it would be integral to have a more regional model that can track how electoral college votes would be cast in each state. Based upon each state’s electoral college system.

Another area of improvement is that the independent variables for this study were selected based upon researcher assumption as to what demographic variables would be likely to influence the election. This introduces a lot of bias to the analysis process and could be improved.

Future studies could take a pre-analysis step where a brief Anova is run across all the possible independent variables included in the Nation Scape Data Set. That way if there are less obvious variables that have more significant predictive effects they could be found and included in the analysis. Or if there are variables that would go against the researchers biases they would be easier to identify.

This helps to remove the researcher from the selection process so that the data is able to speak for itself.

Having a collection of follow up studies that could dig deep into; the lower significance higher income plays in political decision making, what factors are leading the extremely significant and strong racial effects of this election, and why there is an uptick in Biden support with in the age range of 56-75 could yield interesting results. Furthermore, having an overarching study that used pre-analysis, a Nested Bayes model, and adjusted for the effects of the electoral college could identify further voter groups of interest.

@@

# References
- R Core Team (2020). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna,
  Austria. URL https://www.R-project.org/.
- Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43), 1686, https://doi.org/10.21105/joss.01686
- Hadley Wickham, Romain François, Lionel Henry and Kirill Müller (2020). dplyr: A Grammar of Data Manipulation. R package version
  1.0.2. https://CRAN.R-project.org/package=dplyr
- Douglas Bates, Martin Maechler, Ben Bolker, Steve Walker (2015). Fitting Linear Mixed-Effects Models Using lme4. Journal of
  Statistical Software, 67(1), 1-48. doi:10.18637/jss.v067.i01.
- Jared E. Knowles and Carl Frederick (2020). merTools: Tools for Analyzing Mixed Effect Regression Models. R package version 0.5.2.
  https://CRAN.R-project.org/package=merTools
- Hadley Wickham, Jim Hester and Romain Francois (2018). readr: Read Rectangular Text Data. R package version 1.3.1.
  https://CRAN.R-project.org/package=readr
- Yihui Xie (2020). knitr: A General-Purpose Package for Dynamic Report Generation in R. R package version 1.29.
- Yihui Xie (2015) Dynamic Documents with R and knitr. 2nd edition. Chapman and Hall/CRC. ISBN 978-1498716963
- Yihui Xie (2014) knitr: A Comprehensive Tool for Reproducible Research in R. In Victoria Stodden, Friedrich Leisch and Roger D.
  Peng, editors, Implementing Reproducible Computational Research. Chapman and Hall/CRC. ISBN 978-1466561595
- Hadley Wickham and Evan Miller (2020). haven: Import and Export 'SPSS', 'Stata' and 'SAS' Files. R package version 2.3.1.
  https://CRAN.R-project.org/package=haven
- JJ Allaire and Yihui Xie and Jonathan McPherson and Javier Luraschi and Kevin Ushey and Aron Atkins and Hadley Wickham and Joe Cheng
  and Winston Chang and Richard Iannone (2020). rmarkdown: Dynamic Documents for R. R package version 2.3. URL
  https://rmarkdown.rstudio.com.
- Yihui Xie and J.J. Allaire and Garrett Grolemund (2018). R Markdown: The Definitive Guide. Chapman and Hall/CRC. ISBN 9781138359338.
  URL https://bookdown.org/yihui/rmarkdown.
- Monica Alexander. (2019, September 07). Analyzing name changes after marriage using a non-representative survey. Retrieved from https://www.monicaalexander.com/posts/2019-08-07-mrp/
- The New York Times. (n.d.). 2016 Presidential Election Results: Donald J. Trump Wins. Retrieved from https://www.nytimes.com/elections/2016/results/president
- US Census Bureau. (2020, October 16). Population. Retrieved from https://www.census.gov/topics/population.html
- NCSL. (2020). The Electoral College. Retrieved from https://www.ncsl.org/research/elections-and-campaigns/the-electoral-college.aspx
- Financial Times. (2020, October 30). Biden vs Trump: US presidential election poll tracker. Retrieved from https://ig.ft.com/us-election-2020/
- Survey Systems (2020). “Sample Size Calculator.” Sample Size Calculator - Confidence Level, Confidence Interval, Sample Size, Population Size, Relevant Population - Creative Research Systems, 2020, www.surveysystem.com/sscalc.htm.
- Amy Sorkin, John Cassidy, & Jonathan Blitzer. (2018). Donald Trump Compounds His "Shithole Countries" Bigotry with Lies. Retrieved from https://www.newyorker.com/news/daily-comment/donald-trump-compounds-his-shithole-countries-bigotry-with-lies
- Philip Bump. (2020, September 30). Analysis | Donald Trump doesn't really care about the white supremacist threat, and you're not going to make him. Retrieved from https://www.washingtonpost.com/politics/2020/09/30/donald-trump-doesnt-really-care-about-white-supremacy-youre-not-going-make-him/
- Kevin Liptak, & Kristen Holmes. (2020, July 01). Trump calls Black Lives Matter a 'symbol of hate' as he digs in on race. Retrieved from https://www.cnn.com/2020/07/01/politics/donald-trump-black-lives-matter-confederate-race/index.html

>>>>

In this report, we will be forecasting the winner of the upcoming US Presidential Elections 2020 between incumbent Donald Trump of the Republican Party and Joe Biden of the Democratic Party, by looking at different factors that affect a citizen’s voting intentions leading to Election Day. We cleaned the Nationscape dataset and chose the variables age, education, race, family income, geographic region, and mask-wearing decision which will form the basis of our Elections prediction. Then we used an MRP model (a combination of multilevel logistic regression and post-stratification) to analyse the factors and it also helps us in achieving a much narrower confidence interval for our prediction. After our analysis, we concluded that Joe Biden will win the overall popular vote of the 2020 American presidential election.

@@

The US 2020 Election is considered by many to be one of the most crucial elections in recent history. American voters will be deciding to elect Democratic Leader, Joe Biden or Republican leader, Donald Trump. In this report, we will be forecasting the results of the US 2020 election using multi-level regression with post stratification.

We are interested in finding out who will win the overall popular vote in the US 2020 election between Donald Trump and Joe Biden. To begin, we started by cleaning the dataset provided by Nationscape. The data we are using was collected from June 25th, 2020 to July 1st, 2020. Using the dataset, we plan to closely analyze the following variables to use them as predictors in predicting the results of the 2020 US election:
-	X
-	X
-	X
-	X
After using multi-level regression with post stratification, we determined that Joe Biden will be the winner of the US 2020 Election. Predicting the results of the US 2020 election is important because it helps give those residing in the USA certainty about who their next president will be. Information about the winner of the election is highly sought after because it can be used to predict upcoming policy. This is useful for individuals and organizations when planning their lives and can have a large impact on the rights of some individuals.  Additionally, collecting information related to the election allows us to analyze different demographic groups and determine how they are voting to further identify areas they find important; this information is important from a policy design perspective and also to analyze how society is interacting.

In this report, we will begin by discussing the data and then modeling our results. Lastly, we will discuss the results of our analysis and include an appendix.

@@

The variables that we used in our dataset are as follow: 
-	age
     o	“What is your age”
     o	It provides an integer value greater than or equal to 18
-	education
     o	“What is the highest level of education you have completed?” 
     o	An extensive list of options are provided
-	Hispanic
     o	“Are you of Hispanic, Latino, or Spanish origin?” 
     o	An extensive list of options are provided 
-	household_income
     o	“What is your current annual household income before taxes?" 
     o	Provides an extensive list of options beginning with $5,000 increments and then increases to $25,000 increments
     o	This is the variable in our dataset that many people did not feel comfortable answering and was left as N/A. When        cleaning the dataset, we removed all responses that left this answer as N/A  
-	race_ethnicity
     o	“What is your race”
     o	An extensive list of options are provided. 
-	extra_covid_worn_mask
     o	“Have you done any of the following in the past week? - Worn a mask when going out in public” 
     o	Yes or No options are available for the respondent to fill out 
-	state
     o	“Respondent’s state, as a two-character postal abbreviation. Calculated based on entered ZIP code.” 
     o	Manually filled out by respondent 
-	trump_biden
     o	“If the general election for president of the United States was a contest between Joe Biden and Donald Trump, who        would you support? “ 
     o	Options are either ‘Joe Biden’, ‘Donald Trump’, or ‘Don’t Know’

We created an additional variable called ‘binary’ which outputs the result of the variable ‘trump_biden’ as a 1 or a 0 making it binary, therefore easier to analyze. Since some variables had an extensive list of options (e.g. age, household income), we grouped the responses for those variables so that they are simpler and easier to analyze.

@@

In Figure [] below, we can see that the distribution is largely skewed towards families with income less than $50,000:
```{r}
# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
incomeinfo <- tbdata %>% group_by(household_income_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
incomegraph <- incomeinfo %>% ggplot(aes(x = "", y = prop, fill = household_income_grouped)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Accent") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "Survey Distribution of Household Income", fill="Household Income") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
     theme(text = element_text(size=15))
incomegraph
```
Because of the skewed distribution of income, we can justify using post stratification. Clearly, those with income less than $50,000 are overrepresented in the dataset as they take up 50% of the responses, therefore it is appropriate to use post stratification.

We can see a similar skewed distribution in Figure [] below: 
```{r}
# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
raceinfo <- tbdata %>% group_by(race_ethnicity) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
racegraph <- raceinfo %>% ggplot(aes(x = "", y = prop, fill = race_ethnicity)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Set3") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "Survey Distribution of Respondent Race", fill="What is your race?") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4) +
     theme(text = element_text(size=13))
racegraph
```
Looking at the distribution of race, we can see that 75% of the respondants from the survey are white. Since the distribution does not represent minorities, we can justify using post stratification.

Lastly, in Figure [] below, we can see how the population aged older than 76 are barely represented: 
```{r}
# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
ageinfo <- tbdata %>% group_by(age_group) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
agegraph <- ageinfo %>% ggplot(aes(x = "", y = prop, fill = age_group)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Set3") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "Survey Distribution of Respondent Age", fill="Age Groups") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4)+
     theme(text = element_text(size=13))
agegraph
```
The fact that those age 76+ make up only a 3% of the data could be a product of the fact that the survey was completed online. Clearly, the survey doesn't accurately represent those aged older than 76 posing the question — does our data represent the United States? The answer is no. To adjust for the fact that the population aged 76+, we will use post stratification.

The dataset that we used contains many key features. Many of the variables in the dataset contain an extensive list of options assuring us that the data represents the participant's view accurately. Despite the fact that we cleaned the dataset to make it simpler to view, we still believe that the detailed responses that the participants provided accurately reflect their views on the 2020 election, making our analysis meaningful. Another key feature is the fact that the data was collected over a short period of time— from June 25th, 2020 to July 1st, 2020. This significantly reduces the negative time based effects that may have affected the data ensuring that all respondents are responding on a similar ground and no one's opinion dramatically differed due to the survey taking place over a large period of time.

The dataset we used contains many strengths and weaknesses. One of the strengths is due to the fact that the survey is distributed online. In today’s age where most things are online, this ensures that we can reach a wide part of the United States. At the same time, this can also be viewed as a weakness because certain age groups of the United States may not be tech-savvy enough to complete an online survey. The older population of the united states (e.g. 75+) may not be able to complete the survey because it is online which means that our data may not accurately reflect the older populations views regarding the 2020 election. A potential solution to this weakness is to use administer multiple forms of the survey to ensure that all people can access the survey.

Another weakness of the data comes from the fact that we use convenience-based sampling which inherently contains bias. Because the sampling method is based on convenience, we may be unlucky when sampling and get a sample group that inaccurately represents the population of the US making our results meaningless.

Lastly another weakness of our dataset is due to the fact that the survey data we are analyzing is collected from June 25th, 2020 to July 1st, 2020. Between July and November (the month of the election), many voters may not have an informed vote and their opinions may still be swayed after watching crucial debates and hearing what the leaders have to say; our data doesn’t take into consideration the people whose votes may change in the most crucial months of the election. A solution to this weakness can be to analyze data that may have occurred closer to the actual election so that the participants have an informed vote.

@@

## Figure 4
```{r}
acs <- read_dta("post_strat_data-2.dta")
acs <- labelled::to_factor(acs)
incomeinfoacs <- acs %>% group_by(household_income_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
incomegraphacs <- incomeinfoacs %>% ggplot(aes(x = "", y = prop, fill = household_income_grouped)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Accent") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "ACS Distribution of Household Income", fill="Household Income") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
     theme(text = element_text(size=15))

@@

## Figure 5
```{r}
ageinfoacs <- acs %>% group_by(age_group) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
agegraphacs <- ageinfoacs %>% ggplot(aes(x = "", y = prop, fill = age_group)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Accent") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "ACS Distribution of Respondent Age", fill="Household Income") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
     theme(text = element_text(size=15))

@@

## Figure 6
```{r}
raceinfoacs <- acs %>% group_by(race_ethnicity) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
racegraphacs <- raceinfoacs %>% ggplot(aes(x = "", y = prop, fill = race_ethnicity)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Accent") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "ACS Distribution of Respondent Race", fill="Household Income") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
     theme(text = element_text(size=15))

@@

## Table 6
```{r}
Table6 <- post_strat_cellcount_2 %>% 
  dplyr::select(
    age_group, race_ethnicity, household_income_grouped, n, prop
  ) %>% 
  head() %>% 
  kable(align = "c",
        format = "simple",
        col.names = c("Age Group", "Race", "Household Income", "Number of Repondents", "Proportion of Responses"),
        digits = 6
        ) 
Table6
```

@@

```{r include=FALSE}
aggregate(tbdata[8], list(tbdata$race_ethnicity), mean)

```

@@

### 1: Nested Bayesian Model

### 2: Pre-analysis

@@

# References
